Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2017-01-13 removals/manuscript/removal_ms.tex
Bibtek problems
Final edits to ms.

The small competitive release of many species in our system implies that each of the four dominant species we studied are limited by quite different factors. This low niche overlap could reflect strong resource partitioning (Tilman 1982), perhaps combined with variation in the times and locations at which species are taking up those resources. Species-specific responses to spatial and temporal variation in non-resource environmental variables can also weaken interspecific interactions \citep{chesson_mechanisms_2000}, though in a previous study we failed to find evidence of a temporal storage effect in this community \citep{adler_weak_2009}. Interactions with above- or belowground enemies can regulate populations and, given enough species-specificity in the effects of these enemies, decouple interspecific dynamics \citep{hersh_evaluating_2011,janzen_herbivores_1970,connell_role_1971}.  More likely, plants may alter the environment, and even resource availability, in ways that facilitate their neighbors. For example, shade cast by \textit{{A. tripartita} canopies may reduce evapotranspiration (e.g. \citealt{Barbier2008}). \textit{{A. tripartita} removal might offset this facilitative effect by reducing resource uptake, resulting in little net change in water balance following removal.  Unfortunately, we did not monitor soil moisture at the fine spatial and temporal resolution necessary to test this hypothesis.

@@

%\newpage
\bibliographystyle{Ecology}
\bibliography{IPMrefs}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:32:17 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{A. tripartita} survival model. ``logarea" is the effect of plant size, ``Treatment*" is the removal effect, and the ``W.*" coefficients 
are effects of neighborhood crowding (the $\omega$s in eqn. \ref{eqn:survReg}). ``quant" refers to quantile and ``kld" reports the Kullback-Leibler divergence between the Gaussian and the (simplified)Laplace approximation to the marginal posterior densities. } 
\label{ARTRsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & -0.0207 & 0.2261 & -0.4554 & -0.0246 & 0.4367 & -0.0321 & 0.0000 \\ 
  logarea & 0.7208 & 0.0575 & 0.6109 & 0.7195 & 0.8378 & 0.7171 & 0.0000 \\ 
  TreatmentNo\_grass & -1.3218 & 0.7343 & -2.7293 & -1.3340 & 0.1563 & -1.3591 & 0.0000 \\ 
  W.ARTR & -1.5214 & 0.2075 & -1.9391 & -1.5179 & -1.1237 & -1.5107 & 0.0000 \\ 
  W.HECO & -0.0694 & 0.0423 & -0.1485 & -0.0708 & 0.0178 & -0.0738 & 0.0000 \\ 
  W.POSE & -0.0049 & 0.0761 & -0.1469 & -0.0077 & 0.1525 & -0.0134 & 0.0000 \\ 
  W.PSSP & 0.0281 & 0.0275 & -0.0235 & 0.0271 & 0.0849 & 0.0252 & 0.0000 \\ 
  W.allcov & -0.0055 & 0.0083 & -0.0219 & -0.0054 & 0.0109 & -0.0054 & 0.0000 \\ 
  W.allpts & 0.1694 & 0.1579 & -0.1386 & 0.1686 & 0.4812 & 0.1672 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:34:30 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{Poa secunda} survival model (see Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers).} 
\label{POSEsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.3162 & 0.1965 & 0.9242 & 1.3171 & 1.7024 & 1.3186 & 0.0000 \\ 
  logarea & 1.0585 & 0.0640 & 0.9365 & 1.0569 & 1.1902 & 1.0537 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.2572 & 0.1723 & -0.5949 & -0.2573 & 0.0811 & -0.2576 & 0.0000 \\ 
  W.ARTR & 0.0001 & 0.0019 & -0.0036 & 0.0001 & 0.0038 & 0.0001 & 0.0000 \\ 
  W.HECO & -0.0153 & 0.0138 & -0.0424 & -0.0154 & 0.0119 & -0.0154 & 0.0000 \\ 
  W.POSE & -1.2632 & 0.0816 & -1.4260 & -1.2623 & -1.1053 & -1.2605 & 0.0000 \\ 
  W.PSSP & 0.0249 & 0.0122 & 0.0011 & 0.0249 & 0.0490 & 0.0247 & 0.0000 \\ 
  W.allcov & -0.0024 & 0.0026 & -0.0075 & -0.0024 & 0.0029 & -0.0024 & 0.0000 \\ 
  W.allpts & 0.0018 & 0.0524 & -0.1009 & 0.0018 & 0.1048 & 0.0017 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:58 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{Poa secunda} growth model (see Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers).} 
\label{POSEgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4923 & 0.0681 & 0.3581 & 0.4923 & 0.6259 & 0.4924 & 0.0000 \\ 
  logarea.t0 & 0.6750 & 0.0232 & 0.6292 & 0.6750 & 0.7203 & 0.6751 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2161 & 0.0644 & 0.0897 & 0.2161 & 0.3425 & 0.2161 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0019 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0039 & 0.0063 & -0.0084 & 0.0039 & 0.0161 & 0.0039 & 0.0000 \\ 
  W.POSE & -0.2641 & 0.0387 & -0.3400 & -0.2641 & -0.1883 & -0.2641 & 0.0000 \\ 
  W.PSSP & -0.0073 & 0.0056 & -0.0183 & -0.0073 & 0.0038 & -0.0073 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0254 & 0.0231 & -0.0709 & -0.0254 & 0.0200 & -0.0254 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

The small competitive release of many species in our system implies that each of the four dominant species we studied are limited by quite different factors. This low niche overlap could reflect strong resource partitioning (Tilman 1982), perhaps combined with variation in the times and locations at which species are taking up those resources. Species-specific responses to spatial and temporal variation in non-resource environmental variables can also weaken interspecific interactions \citep{chesson_mechanisms_2000}, though in a previous study we failed to find evidence of a temporal storage effect in this community \citep{adler_weak_2009}. Interactions with above- or belowground enemies can regulate populations and, given enough species-specificity in the effects of these enemies, decouple interspecific dynamics \citep{hersh_evaluating_2011,janzen_herbivores_1970,connell_role_1971}.  More likely, plants may alter the environment, and even resource availability, in ways that facilitate their neighbors. For example, shade cast by \textit{A. tripartita} canopies may reduce evapotranspiration (e.g. \citealt{Barbier2008}). \textit{A. tripartita} removal might offset this facilitative effect by reducing resource uptake, resulting in little net change in water balance following removal.  Unfortunately, we did not monitor soil moisture at the fine spatial and temporal resolution necessary to test this hypothesis.

@@

%\newpage
\bibliographystyle{Ecology}
\bibliography{RemovalRefs}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:32:17 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{A. tripartita} survival model. ``logarea" is the effect of plant size, ``Treatment*" is the removal effect, and the ``W.*" coefficients 
are effects of neighborhood crowding (the $\omega$s in eqn. \ref{eqn:survReg}). ``quant" refers to quantile and ``kld" reports the Kullback-Leibler divergence between the Gaussian and the (simplified) Laplace approximation to the marginal posterior densities. } 
\label{ARTRsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & -0.0207 & 0.2261 & -0.4554 & -0.0246 & 0.4367 & -0.0321 & 0.0000 \\ 
  logarea & 0.7208 & 0.0575 & 0.6109 & 0.7195 & 0.8378 & 0.7171 & 0.0000 \\ 
  TreatmentNo\_grass & -1.3218 & 0.7343 & -2.7293 & -1.3340 & 0.1563 & -1.3591 & 0.0000 \\ 
  W.ARTR & -1.5214 & 0.2075 & -1.9391 & -1.5179 & -1.1237 & -1.5107 & 0.0000 \\ 
  W.HECO & -0.0694 & 0.0423 & -0.1485 & -0.0708 & 0.0178 & -0.0738 & 0.0000 \\ 
  W.POSE & -0.0049 & 0.0761 & -0.1469 & -0.0077 & 0.1525 & -0.0134 & 0.0000 \\ 
  W.PSSP & 0.0281 & 0.0275 & -0.0235 & 0.0271 & 0.0849 & 0.0252 & 0.0000 \\ 
  W.allcov & -0.0055 & 0.0083 & -0.0219 & -0.0054 & 0.0109 & -0.0054 & 0.0000 \\ 
  W.allpts & 0.1694 & 0.1579 & -0.1386 & 0.1686 & 0.4812 & 0.1672 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:34:30 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} survival model (see Table \ref{ARTRsurvival} for an explanation of coefficient names
and column headers).} 
\label{POSEsurvival}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 1.3162 & 0.1965 & 0.9242 & 1.3171 & 1.7024 & 1.3186 & 0.0000 \\ 
  logarea & 1.0585 & 0.0640 & 0.9365 & 1.0569 & 1.1902 & 1.0537 & 0.0000 \\ 
  TreatmentNo\_shrub & -0.2572 & 0.1723 & -0.5949 & -0.2573 & 0.0811 & -0.2576 & 0.0000 \\ 
  W.ARTR & 0.0001 & 0.0019 & -0.0036 & 0.0001 & 0.0038 & 0.0001 & 0.0000 \\ 
  W.HECO & -0.0153 & 0.0138 & -0.0424 & -0.0154 & 0.0119 & -0.0154 & 0.0000 \\ 
  W.POSE & -1.2632 & 0.0816 & -1.4260 & -1.2623 & -1.1053 & -1.2605 & 0.0000 \\ 
  W.PSSP & 0.0249 & 0.0122 & 0.0011 & 0.0249 & 0.0490 & 0.0247 & 0.0000 \\ 
  W.allcov & -0.0024 & 0.0026 & -0.0075 & -0.0024 & 0.0029 & -0.0024 & 0.0000 \\ 
  W.allpts & 0.0018 & 0.0524 & -0.1009 & 0.0018 & 0.1048 & 0.0017 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.8-2 package
% Mon Sep 19 08:36:58 2016
\begin{table}[ht]
\centering
\caption{Summary of fixed effects for the \textit{P. secunda} growth model (see Table \ref{ARTRgrowth} for an explanation of coefficient names
and column headers).} 
\label{POSEgrowth}
\begin{tabular}{rrrrrrrr}
  \hline
 & mean & sd & 0.025quant & 0.5quant & 0.975quant & mode & kld \\ 
  \hline
(Intercept) & 0.4923 & 0.0681 & 0.3581 & 0.4923 & 0.6259 & 0.4924 & 0.0000 \\ 
  logarea.t0 & 0.6750 & 0.0232 & 0.6292 & 0.6750 & 0.7203 & 0.6751 & 0.0000 \\ 
  TreatmentNo\_shrub & 0.2161 & 0.0644 & 0.0897 & 0.2161 & 0.3425 & 0.2161 & 0.0000 \\ 
  W.ARTR & -0.0002 & 0.0008 & -0.0019 & -0.0002 & 0.0014 & -0.0002 & 0.0000 \\ 
  W.HECO & 0.0039 & 0.0063 & -0.0084 & 0.0039 & 0.0161 & 0.0039 & 0.0000 \\ 
  W.POSE & -0.2641 & 0.0387 & -0.3400 & -0.2641 & -0.1883 & -0.2641 & 0.0000 \\ 
  W.PSSP & -0.0073 & 0.0056 & -0.0183 & -0.0073 & 0.0038 & -0.0073 & 0.0000 \\ 
  W.allcov & -0.0003 & 0.0012 & -0.0026 & -0.0003 & 0.0020 & -0.0003 & 0.0000 \\ 
  W.allpts & -0.0254 & 0.0231 & -0.0709 & -0.0254 & 0.0200 & -0.0254 & 0.0000 \\ 
   \hline
\end{tabular}
\end{table}
